Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

The goal of this experiment is to verify the accuracy of complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex} 
by observing the effects the hyper-parameters of the GNN on training time-consuming and memory usage.

@@

Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
Its time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
the GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
This phenomenon confirms the necessity of removing abnormal epochs.

@@

GaAN also uses a multi-head mechanism, and its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is affected by hyperparameters.
The experiment verifies the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. The training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
When the hidden vector dimension $d_(in)$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.

Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's use of GPU memory varies with the algorithm's hyperparameters.
With the increase of hyperparameters, GNN's memory usage has also increased linearly.

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset itself)}
	\label{fig:exp_hyperparameter_memory_usage}
\end{figure}

The experiment verifies the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN Without worrying about the time-consuming training and the explosive growth of memory usage.

@@

For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each algorithm
to the total training time (including forward, backward and evaluation stages). The GCN algorithm takes the most time to calculate on most datasets, 
only the cph dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
ratio significantly higher than other algorithms, but on most datasets, edge calculation still occupies the main calculation time-consuming. 
Only in pub and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost Time is absolutely dominant. 
In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.

@@

We performed the execution time decomposition of the edge calculation process of each GNN algorithm on different datasets,
and the results are shown in Fig~\ref{fig:exp_edge_calc_decomposition}.
The time-consuming decomposition of the edge calculation of each GNN is relatively stable, 
and the dataset correlation is not strong. Although the collect step only performs data preparation,
it occupies a lot of execution time in all GNNs. For the message step, in the GNN (GAT and GaAN) with high edge calculation complexity, 
Which occupies the absolute dominant. Although its side calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
In GGNN, because its side calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase),
the calculated result is cached, and it is directly read when the message step is performed The result is that the message step of GGNN takes 0.
For the aggregate step, it occupies at least 35\% of the time-consuming GNN (GCN and GGNN) with low computational complexity,
while the GNN with high computational complexity ( GAT and GaAN), whose time consumption is close to the collect step,
and both are much lower than the message step. Experiments show that \textbf{for an algorithm with high edge calculation complexity,
the message step is the bottleneck of its performance, and it should be optimized}; and \textbf{For algorithms with low computational complexity,
optimizing the collect and aggregate steps can significantly reduce training time}.

@@

\begin{enumerate}
    \item The matrix multiplication operator mm in GCN is mainly used for vertex calculation $\gamma$, 
    this operator is particularly time-consuming on the cph dataset, 
    because the dimensionality of the vertex feature vector input by cph is very high,
    making the matrix multiplication in the vertex calculation of Layer0 The calculation is very high.
    Mul is the multiplication operation in the edge calculation function $\phi$.
    Both scatter\_add and gather are used to implement the aggregation step $\Sigma$ in the edge calculation,
    where the former is used in the forward stage and the latter is used in backward Phase.
    The index\_select operator is used in the collect step of the edge calculation.
    For the GCN algorithm, the edge calculation related operators occupy the main time-consuming.
    The time-consuming among the operators is relatively average, and there is no particularly outstanding performance bottleneck.
    \item The most time consuming in GGNN is also the matrix multiplication mm operator,
    which is mainly used for the vertex calculation function $\gamma$. The scatter\_add, index\_select and gather operators
    are used for edge calculations. And the \_thnn\_fused\_gru\_cell is used in the backward calculation of GRU.
    GGNN because of vertices With the increase in calculation complexity, the time-consuming time of the mm operator has increased significantly.
    \item The four most time-consuming operators in GAT are all related to the edge calculation. 
    Mul, \_index\_put\_impl and sum are used to implement the edge calculation function $\phi$.
    The index\_select operator is used in the collect phase of the edge calculation. 
    The mm operator is used vertex calculation function $\gamma$.
    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and edge calculation,
    where edge calculation is dominant. Mul and cat are used for the $\phi$ function in edge calculation.
\end{enumerate}

In terms of commonality, 
\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, multiplication of mul and other operators by the number of elements},
so it is very suitable for calculation with GPU. Although the calculation of the aggregate step in edge calculation is relatively simple,
but Because it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
the related operators scatter\_add and gather still occupy a certain amount of time.
Although the collection step in the side calculation does not have any calculations,
but the related calculations The index\_select operator still accounts for about 10\% of the time-consuming.
\textbf{aggregate step and collect step are one of the computational performance bottlenecks of all GNN training},
optimizing the corresponding operator will improve the training efficiency of all GNNs.

@@

\begin{itemize}
    \item \textbf{The performance bottleneck of GNN training is affected by the average degree of the dataset}. 
    Because the average degree of most real-world graphs is above 10 degrees \cite{network-repository}, 
    the performance bottleneck of GNN training will be concentrated on the edges Calculation section.
    \item \textbf{According to the calculation complexity of the edge calculation function $\phi$, the performance bottleneck of GNN in edge calculation is different}:
    \begin{itemize}
        \item If the computational complexity of $\phi$ is high, the performance bottleneck is concentrated on the basic operators used to implement $\phi$.
        Optimizing the implementation of the corresponding basic operators will improve the training performance of this type of GNN.
        Taking GAT as an example, The most time-consuming operator \_index\_put\_impl in GAT is mainly used in the backward stage of the softmax calculation ($\alpha^k_{ij}$) in $\phi$,
        which only involves data movement.
        The optimized softmax implementation on the GPU can Significantly reduce GAT training time.
        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its side calculations are bottlenecks in computational performance. The collect step only involves a large amount of data movement. The aggregate step calculation is relatively simple (such as sum/average/maximum) Value, etc.), but because it involves data synchronization and irregular calculation, its time-consuming is still significant.
         Optimizing the implementation of these two steps on the GPU will improve the training performance of this type of GNN.
    \end{itemize}
\end{itemize}

@@

At present, all data (including datasets and intermediate calculation results) of PyG in the process of training GNN with GPU
are stored in GPU memory. Compared with the main memory of the system, the memory capacity on GPU is very limited.
\textbf{GPU memory capacity is limited to Determinants of the size of the training dataset}. 
GaAN was unable to complete the training due to memory overflow during the training of the `cph` dataset.

@@

Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
Because the input feature dimension of the cph dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
so its expansion ratio is particularly low, and the cam dataset is the opposite. In order to measure the effect of the input feature vector dimension on the memory
expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .

@@

In the case of a fixed number of vertices in the graph, we use the R-MAT generator to generate random graphs with different average degrees (number of edges).
The Fig~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
\textbf{As the average degree increases, the peak memory usage increases linearly.
The intermediate results generated by the side calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}. 
The expansion ratio is affected by the complexity of the side calculation.
Except for GGNN, the memory expansion ratio of other GNNs increases with the increase of degree. GGNN has a high vertex calculation complexity.
When the average degree is low, its memory expansion ratio is mainly affected by the intermediate results of vertex calculation;
when the average When the degree is increased, the memory expansion ratio is gradually determined by the edge calculation complexity.
Because GGNN has the lowest edge calculation complexity, its stable expansion ratio is the lowest.

@@

It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
The average degree of the amp dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
which is much lower than the average degree of the full picture;
the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
The reason is that the distribution of vertices in the actual graph dataset follows a power-rate distribution, and a small number of vertices The degree is very high,
which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.

@@

Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the `amc` and `fli` datasets with the batch size after using the sampling technique.
For the neighbor sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-picture training. 
When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full image. 
Training is time-consuming. For cluster sampler, the sampled subgraph is smaller than neighbor sampler under the same relative batch size,
which makes the effect of sampling technology more obvious. But when the relative batch size increases, 
the additional cost of sampling technology The increase is very obvious. When the relative batch size $\geq$ 25\%,
the total time of each batch of the sampling technique even exceeds the time of the full image training. 
Experiments show that \textbf{the implementation of sampling technology in PyG at this stage is very inefficient and the extra overhead is high}.
When the batch size is slightly larger, the additional cost of sampling technology accounts for more than 50\% of the total training cost of the entire batch.
\textbf{Sampling technology can reduce training time only on very small batches}.

>>>>

The goal of this experiment is to verify the accuracy of complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex} 
by observing the effects the hyper-parameters of each GNN model on training time per epoch and memory usage.

@@

Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
Its time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
the algorithm GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
This phenomenon confirms the necessity of removing abnormal epochs.

@@

GaAN also uses a multi-head mechanism, and its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is affected by hyperparameters.
The experiment verifies the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. The training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.

Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's GPU memory usage varies with the algorithm's hyperparameters.
With the increase of hyperparameters, GNN's memory usage also increases linearly.

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset memory)}
	\label{fig:exp_hyperparameter_memory_usage}
\end{figure}

The experiment verifies the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN without worrying about the time-consuming training and the explosive growth of memory usage.

@@

For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each algorithm
to the total training time (including forward, backward and evaluation stages). The GCN algorithm takes the most time to calculate on most datasets, 
only the \textit{cph} dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
ratio significantly higher than other algorithms, but on most datasets, edge calculation still occupies the main calculation time-consuming. 
Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost time is absolutely dominant. 
In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.

@@

We performed the execution time decomposition of the edge calculation process of each GNN algorithm on different datasets,
and the results are shown in Fig~\ref{fig:exp_edge_calc_decomposition}.
The time-consuming decomposition of the edge calculation of each GNN is relatively stable, 
and the dataset correlation is not strong. Although the collect step only performs data preparation,
it occupies a lot of execution time in all GNNs. For the message step, in the GNN (GAT and GaAN) with high edge calculation complexity, 
which occupies the absolute dominant. Although its edge calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
In GGNN, because its edge calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase),
the calculated result is cached, and it is directly read when the message step is performed The result is that the message step of GGNN takes 0.
For the aggregate step, it occupies at least 35\% of the time-consuming GNN (GCN and GGNN) with low computational complexity,
while the GNN with high computational complexity ( GAT and GaAN), whose time consumption is close to the collect step,
and both are much lower than the message step. Experiments show that \textbf{for an algorithm with high edge calculation complexity,
the message step is the bottleneck of its performance, and it should be optimized}; and \textbf{For algorithms with low computational complexity,
optimizing the collect and aggregate steps can significantly reduce training time}.

@@

\begin{enumerate}
    \item The matrix multiplication operator mm in GCN is mainly used for vertex calculation $\gamma$, 
    this operator is particularly time-consuming on the \textit{cph} dataset, 
    because the dimensionality of the vertex feature vector input by \textit{cph} is very high,
    making the matrix multiplication in the vertex calculation of Layer0 The calculation is very high.
    Mul is the multiplication operation in the edge calculation function $\phi$.
    Both scatter\_add and gather are used to implement the aggregation step $\Sigma$ in the edge calculation,
    where the former is used in the forward stage and the latter is used in backward Phase.
    The index\_select operator is used in the collect step of the edge calculation.
    For the GCN algorithm, the edge calculation related operators occupy the main time-consuming.
    The time-consuming among the operators is relatively average, and there is no particularly outstanding performance bottleneck.
    \item The most time consuming in GGNN is also the matrix multiplication mm operator,
    which is mainly used for the vertex calculation function $\gamma$. The scatter\_add, index\_select and gather operators
    are used for edge calculations. And the \_thnn\_fused\_gru\_cell is used in the backward calculation of GRU.
    GGNN because of vertices With the increase in calculation complexity, the time-consuming time of the mm operator has increased significantly.
    \item The four most time-consuming operators in GAT are all related to the edge calculation. 
    Mul, \_index\_put\_impl and sum are used to implement the edge calculation function $\phi$.
    The index\_select operator is used in the collect phase of the edge calculation. 
    The mm operator is used vertex calculation function $\gamma$.
    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and edge calculation,
    where edge calculation is dominant. Mul and cat are used for the $\phi$ function in edge calculation.
\end{enumerate}

In terms of commonality, 
\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, multiplication of mul and other operators by the number of elements},
so it is very suitable for calculation with GPU. Although the calculation of the aggregate step in edge calculation is relatively simple,
but Because it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
the related operators scatter\_add and gather still occupy a certain amount of time.
Although the collection step in the edge calculation does not have any calculations,
but the related calculations The index\_select operator still accounts for about 10\% of the time-consuming.
\textbf{aggregate step and collect step are one of the computational performance bottlenecks of all GNN training},
optimizing the corresponding operator will improve the training efficiency of all GNNs.

@@

\begin{itemize}
    \item \textbf{The performance bottleneck of GNN training is affected by the average degree of the dataset}. 
    Because the average degree of most real-world graphs is above 10 degrees \cite{network-repository}, 
    the performance bottleneck of GNN training will be concentrated on the edges Calculation section.
    \item \textbf{According to the calculation complexity of the edge calculation function $\phi$, the performance bottleneck of GNN in edge calculation is different}:
    \begin{itemize}
        \item If the computational complexity of $\phi$ is high, the performance bottleneck is concentrated on the basic operators used to implement $\phi$.
        Optimizing the implementation of the corresponding basic operators will improve the training performance of this type of GNN.
        Taking GAT as an example, The most time-consuming operator \_index\_put\_impl in GAT is mainly used in the backward stage of the softmax calculation ($\alpha^k_{ij}$) in $\phi$,
        which only involves data movement.
        The optimized softmax implementation on the GPU can Significantly reduce GAT training time.
        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its edge calculations are bottlenecks in computational performance. The collect step only involves a large amount of data movement. The aggregate step calculation is relatively simple (such as sum/average/maximum) Value, etc.), but because it involves data synchronization and irregular calculation, its time-consuming is still significant.
         Optimizing the implementation of these two steps on the GPU will improve the training performance of this type of GNN.
    \end{itemize}
\end{itemize}

@@

At present, all data (including datasets and intermediate calculation results) of PyG in the process of training GNN with GPU
are stored in GPU memory. Compared with the main memory of the system, the memory capacity on GPU is very limited.
\textbf{GPU memory capacity is limited to Determinants of the size of the training dataset}. 
GaAN was unable to complete the training due to memory overflow during the training of the `\textit{cph}` dataset.

@@

Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
Because the input feature dimension of the \textit{cph} dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
so its expansion ratio is particularly low, and the cam dataset is the opposite. In order to measure the effect of the input feature vector dimension on the memory
expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .

@@

In the case of a fixed number of vertices in the graph, we use the R-MAT generator to generate random graphs with different average degrees (number of edges).
The Fig~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
\textbf{As the average degree increases, the peak memory usage increases linearly.
The intermediate results generated by the edge calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}. 
The expansion ratio is affected by the complexity of the edge calculation.
Except for GGNN, the memory expansion ratio of other GNNs increases with the increase of degree. GGNN has a high vertex calculation complexity.
When the average degree is low, its memory expansion ratio is mainly affected by the intermediate results of vertex calculation;
when the average When the degree is increased, the memory expansion ratio is gradually determined by the edge calculation complexity.
Because GGNN has the lowest edge calculation complexity, its stable expansion ratio is the lowest.

@@

It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
which is much lower than the average degree of the full picture;
the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
The reason is that the distribution of vertices in the actual graph dataset follows a power-rate distribution, and a small number of vertices The degree is very high,
which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.

@@

Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
For the neighbor sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-picture training. 
When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full image. 
Training is time-consuming. For cluster sampler, the sampled subgraph is smaller than neighbor sampler under the same relative batch size,
which makes the effect of sampling technology more obvious. But when the relative batch size increases, 
the additional cost of sampling technology The increase is very obvious. When the relative batch size $\geq$ 25\%,
the total time of each batch of the sampling technique even exceeds the time of the full image training. 
Experiments show that \textbf{the implementation of sampling technology in PyG at this stage is very inefficient and the extra overhead is high}.
When the batch size is slightly larger, the additional cost of sampling technology accounts for more than 50\% of the total training cost of the entire batch.
\textbf{Sampling technology can reduce training time only on very small batches}.
